---
title: "emileygz_FinalHomeworkCode_05"
author: "Emiley Garcia-Zych"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    theme: cayman
    toc: true
---

# Homework 5: Boots for Days!

Emiley Garcia-Zych

## [1] Using the "KamilarAndCooperData.csv" dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).

```{r}
library ('curl')
k_and_c <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall23/KamilarAndCooperData.csv")
d <- read.csv(k_and_c, header = TRUE, sep = ",", stringsAsFactors = FALSE)
d <- na.omit(d) ## omit incomplete data
head(d)
```

```{r}
## log(HomeRange_km2) ~ log(Body_mass_female_mean)
##model <- lm(HomeRange_km2 ~ Body_mass_female_mean, data = d) 
model <- lm(log(HomeRange_km2) ~ log(Body_mass_female_mean), data = d) ##changed according to peer review
summary_lm <- summary(model)
slope_estimate <- summary_lm["coefficients"] ##calculate slope
slope_estimate

confint(model, level = 0.95)
```

Slope = -9.750245

Intercept = 1.086790

## [2] Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.

```{r}
#load required library 
##method obtained from https://www.statmethods.net/advstats/bootstrapping.html
library(boot)
#create a function for model fitting + bootstrapping 
#boot fucntion : bootobject <- boot(data = , statistic = , R=, ...)
boot_lm <- function (data, indices) {
  sample_data <- data[indices, ]
  model1<- lm(log(HomeRange_km2) ~ log(Body_mass_female_mean), data = sample_data)
  return(coef(model1))
}

#perform bootstrapping 
boot_results <- boot(data = d, statistic = boot_lm, R = 1000)

#get bootstrapped coefficients
boot_coeff <- boot_results$t

#summarize bootstrapped coefficients
summary(boot_coeff)

##outputs: V1 is vector 1 (log(HomeRange_km2)), V2 is vector 2(log(Body_mass_female_mean))
```

## [3] Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap and determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.

```{r}
##calculate standard errors
##the apply function allows you to repetitively perform an action on multiple chunks of data. Essentially a loop. Based on description in https://ademos.people.uic.edu/Chapter4.html
se_bootstrap <- apply(boot_coeff, 1, sd)
summary(se_bootstrap)

ci_bootstrap <- apply(boot_coeff, 2, sd)
summary(ci_bootstrap)
```

### [3a] How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?

The standard error values estimated from the linear regression model are lower than the computed SE in part 2.

### [3b] How does the latter compare to the 95% CI estimated from your entire dataset?

The 95% CI estimated in part 3 is smaller than the CI calculated in part 2.

## Challenges

1) I struggled with the initial bootstrapping as I kept running into the problem of it only running the first line. I then did research on bootstrapping which cleared it up once I found there was an actual method I could use.

2) I also struggled with understanding how to interpret all my coefficients. I liked how rsibal isolated and printed the data along with its description.

3) Once I decided to switch to code not used in the modules, I struggled to find resources that explained all of it working together. The apply function and bootstrapping both essentially work as big loops so I was able to make it work but I wonder if there is a more effective way to do this.
